```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(rsample)
library(tidymodels)

```
```{r}
car_data <- read_csv("CarPrice.csv") %>%
  glimpse()
```

```{r}
sapply(car_data, function(x) sum(is.na(x)))
```
there is no NA 




```{r}
#Extracting brand name from car name
car_data$CarName <- sapply(strsplit(car_data$CarName, " "), `[`, 1)
car_data$CarName
```

```{r}
#Plotting car name to check the distribution
ggplot(data = car_data, aes(x=CarName, fill = CarName)) +
  geom_bar() +
 labs(x= "car Brand", title= "bar graph of car brand") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```




```{r}
ggplot(data = car_data, aes(x=fueltype, fill = fueltype)) +
  geom_bar() + labs(x="Fuel type") + labs(title = "Bar Graph of Fuel") 
```
Most of the cars fall into gas category. Very few cars fall into diesel category .



```{r}

ggplot(data = car_data, aes(x=carbody, fill = carbody)) +
  geom_bar() + labs(x='car body') + labs(title = "Bar Graph of car body")  
  

```
Most of the cars are sedan .




```{r}
ggplot(data=car_data, aes(x=doornumber, fill=doornumber ))+
  geom_bar()+
  labs(x= "door number", title="Bar Graph of door number")
```




```{r}
ggplot(data=car_data, aes(x=enginetype, fill=enginetype ))+
  geom_bar()+
  labs(x= "engine type", title="Bar Graph of engine type")
```
most of cars are ohc





```{r}
ggplot(car_data, aes(x=horsepower, y=peakrpm)) +
  geom_point()
```



```{r}
ggplot(car_data, aes(x=price)) + 
  geom_histogram(bins=20, colour="white", fill="steelblue")+
  labs(x='Selling Price ') + labs(title = "Histogram Graph of Selling Price") 
```



the mean of engine size  ?
```{r}
car_data%>%
  group_by(CarName)%>%
  summarise(mean=mean(enginesize))
```


nombre de véhicules par fueltype 

```{r}
car_data %>%
  group_by(fueltype) %>%
  summarize(n())
```



what cars have an ohc engine?

```{r}
car_data%>%
  filter(enginetype=="ohc")%>%
  select(CarName, car_ID)
```




sorting cars from more expensive to more cheaper 
```{r}
car_data%>%
  group_by(CarName)%>%
  arrange(desc(price))%>%
  select(car_ID, fueltype, price)
```




Regroupement de nombre de voitures par nom 

```{r}
car_data %>% 
  group_by(CarName) %>% 
  summarise(num_car=n()) %>%
  arrange(desc(num_car))
```
Toyota est la marque ayant le plus grand nombre de voiture dans notre dataset 



étudions la relation entre l'emplacement du moteur et son type
```{r}
car_data %>% 
  filter(enginelocation== "front") %>% 
  group_by(enginelocation, enginetype) %>% 
  summarize(number=n()) 
  #mutate(pourcentage=round (number/sum(number), 2) * 100)
```
les voitures ayant le moteur devant possédent généralement un type ohc



```{r}
car_data$CarName <- str_replace(car_data$CarName, 'alfa-romero', '0')
car_data$CarName <- str_replace(car_data$CarName, 'bmw', '1')
car_data$CarName <- str_replace(car_data$CarName, 'audi', '2')
car_data$CarName <- str_replace(car_data$CarName, 'buick', '3')
car_data$CarName <- str_replace(car_data$CarName, 'chevrolet', '4')
car_data$CarName <- str_replace(car_data$CarName, 'dodge', '5')
car_data$CarName <- str_replace(car_data$CarName, 'honda', '6')
car_data$CarName <- str_replace(car_data$CarName, 'isuzu', '7')
car_data$CarName <- str_replace(car_data$CarName, 'jaguar', '8')
car_data$CarName <- str_replace(car_data$CarName, 'maxda', '9')
car_data$CarName <- str_replace(car_data$CarName, 'mazda', '10')
car_data$CarName <- str_replace(car_data$CarName, 'mercury', '11')
car_data$CarName <- str_replace(car_data$CarName, 'mitsubishi', '12')
car_data$CarName <- str_replace(car_data$CarName, 'nissan', '13')
car_data$CarName <- str_replace(car_data$CarName, 'volkswagen', '14')
car_data$CarName <- str_replace(car_data$CarName, 'peugeot', '15')
car_data$CarName <- str_replace(car_data$CarName, 'plymouth', '16')
car_data$CarName <- str_replace(car_data$CarName, 'porsche', '17')
car_data$CarName <- str_replace(car_data$CarName, 'porcshce', '18')
car_data$CarName <- str_replace(car_data$CarName, 'renault', '19')
car_data$CarName <- str_replace(car_data$CarName, 'saab', '20')
car_data$CarName <- str_replace(car_data$CarName, 'subaru', '21')
car_data$CarName <- str_replace(car_data$CarName, 'toyota', '22')
car_data$CarName <- str_replace(car_data$CarName, 'vw', '23')
car_data$CarName <- str_replace(car_data$CarName, 'volvo', '24')
car_data$CarName <- str_replace(car_data$CarName, 'toyouta', '25')
car_data$CarName <- str_replace(car_data$CarName, 'vokswagen', '26')
car_data$CarName <- str_replace(car_data$CarName, 'Nissan', '27')

#Converting car name from categorical to numerical value

car_data$CarName<- as.numeric(car_data$CarName)
table(car_data$CarName)
```
splitting the data into training and testing


building model :


```{r}
lm_spec <-linear_reg() %>% 
set_engine(engine ="lm") 

```

```{r}
set.seed(100)
new_split <- initial_split(car_data)
new_train <- training(new_split)
new_test <- testing(new_split)

lm_fit <- lm_spec %>%
fit(price ~ CarName+horsepower+enginesize+peakrpm+highwaympg+citympg, data = new_train)
price_pred <- lm_fit %>%
predict(new_data = new_test) %>%
mutate(price_truth = new_test$price)
price_pred

```
```{r}
rmse(price_pred, truth = price_truth, estimate = .pred)
```



model 2 decision tree : 


```{r}

rt_spec <- decision_tree() %>%
set_engine("rpart") %>%
set_mode("regression")

rt_fit <- rt_spec %>%
fit(price ~ CarName+horsepower+enginesize+peakrpm+highwaympg+citympg, data = new_train)
price_pred <- rt_fit%>%
predict(new_test) %>%
mutate(truth = new_test$price) 
price_pred 

rmse(price_pred, truth, .pred)


```

model 3 random forest :


```{r}
rt_spec <- rand_forest() %>%
set_engine("ranger") %>%
set_mode("regression")

rt_fit <- rt_spec %>%
fit(price ~ CarName+horsepower+enginesize+peakrpm+highwaympg+citympg, data = new_train)
price_pred <- rt_fit%>%
predict(new_test) %>%
mutate(truth = new_test$price) 
price_pred 


rmse(price_pred, truth, .pred)
```
Nous allons sélectionner le modèle produit par l’algorithme random forest, car plus le RMSE est petit, plus la capacité du modèle à distinguer la variabilité de la prédiction 
